\documentclass{article}
\linespread{1.3}
\usepackage[margin=50pt]{geometry}
\usepackage{amsmath, amsthm, amssymb, amsthm, tikz, fancyhdr, graphicx}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\changefont}{\fontsize{15}{15}\selectfont}

\fancypagestyle{firstpageheader}
{
  \fancyhead[R]{\changefont Michael Huang \\ CFRM 420 \\ Homework 2}
}

\begin{document}

\thispagestyle{firstpageheader}

\section*{1.}
{\Large 

%\begin{verbatim}
%  Text enclosed inside \texttt{verbatim}
%  environment 
%  is printed directly 
%  and all \LaTeX{} commands are ignored.
%\end{verbatim}
%
%\framebox[1.1\width]{\textbf{answer}}

\subsection*{(a)}

We aim to find $\mathbb{P}(X \in \{3, 4, 5\})$ with $X \sim \text{Poisson}(2)$, or the probability that $X$ is 3, 4, or 5 within the Poisson distribution with $\lambda = 2$. To do this, we can find the respective pdfs and sum them up: \\
$\mathbb{P}(X = 3) = 0.18044704$ \\
$\mathbb{P}(X = 4) = 0.09022352$ \\
$\mathbb{P}(X = 5) = 0.03608941$ \\ 
$\mathbb{P}(X \in \{3, 4, 5\}) = 0.18044704 + 0.09022352 + 0.03608941 = $ \framebox[1.1\width]{\textbf{0.30675997}}

\subsection*{(b)}

We aim to find $\mathbb{P}(Z < -4)$ with $Z \sim \text{N}(0, 1)$. This is the default normal, and we essentially just need to take the cdf of -4, which we can look up / calculate in R to be \framebox[1.1\width]{\textbf{3.167124e-05}}

\subsection*{(c)}

% check and see if this is right for sd_nu adjustment or not
$\mathbb{P}(T / a < -4)$ with $T \sim \text{t}(10)$ and $a = 1.25$; that is, $T$ has a Student's $t$ distribution with 10 degrees of freedom. Again, we take the cdf of -4, which we can look up / calculate in R to be \framebox[1.1\width]{\textbf{0.001259166}}.
% or 0.0005967334

\subsection*{(d)}

The quantities calculated in (b) and (c) are known as the probabilities of a 4-sigma event. Suppose that $Z$ and $T/a$ are the log returns of two different assets. Briefly comment on how much more likely 4-sigma events are for $T/a$ compared to $Z$ and what this reveals about these asset returns. \\ \\
The likelihood of a 4-sigma event, where the log returns are 4 standard deviations below the current value, is much more likely for the heavy-tailed distribution based asset than the normal distribution based asset.

}

\section*{2.}
{\Large

We model the one-day log return for a stock is $t_{t+1} \sim N(0.0006, 0.02^2)$, and the current investment $P_t = \$ 10$ million.

\subsection*{(a)}

We aim to find the value $x$ such that the probability that the investor suffers a one-day log return less than $x$ is $1\%$. Essentially, we want to find $\mathbb{P}(X < x) = 0.01$. We can do this by using the quantile function using the normal as described; calculating this using R we can find this log return value to be \framebox[1.1\width]{\textbf{-0.04592696}}


\subsection*{(b)}

We aim to find the 99\% value-at-risk, which we can do by calculating $-(P_{t+1} - P_t)$. We first calculate $P_{t+1}$. We know log returns is calculated such that \\
$-0.04592696 = \text{ln}(\frac{P_{t+1}}{P_t})$ \\
$e^{-0.04592696} = \frac{P_{t+1}}{P_t}$ \\ 
$e^{-0.04592696} = \frac{P_{t+1}}{10 \text{ million}}$ \\ 
$P_{t+1} = 9.551117 \text{ million}$ \\ \\
$99\% \text{ VAR} = -(P_{t+1} - P_t) = -(9.551117 - 10) \text{ million} = 0.448883 \text{ million} = $ \framebox[1.1\width]{\textbf{\$448,883}}

}

\section*{3.}
{\Large 

Let \textbf{X} = $(X_1, X_2 \sim \text{N}(\boldsymbol{\mu}, \Sigma))$ be a bivariate normal distribution, where \\

$\boldsymbol{\mu} = $
\begin{pmatrix}
1 \\
2	
\end{pmatrix}, 
$\Sigma=$
\begin{pmatrix}
1 & -1.2 \\
-1.2 & 2
\end{pmatrix}.

\subsection*{(a)}

We can show that $\Sigma$ is a valid covariance matrix if it is positive semidefinite. To do this, we can equivalently show that the eigenvalues are greater than or equal to zero. Doing this in R, we see that the eigenvalues for $\Sigma$ are 2.8 and 0.2, both of which are indeed greater than or equal to zero.

\subsection*{(b)}

If $X_1$ and $X_2$ are the one-period log returns of two consecutive periods, explain what $X_1 + X_2$ represents, and find the distribution of $X_1 + X_2$.

We know that $X_1 + X_2$ would represent the total log return across the two consecutive periods, due to the logarithmic nature of the returns. Since $X_1$ and $X_2$ have a bivariate normal distribution, $X_1 + X_2$ would also be a normal distribution, since any linear combination of $X_1$ and $X_2$ would result in a normal distribution. Its distribution would be as follows: \\
$\mu_{X_1 + X_2} = E(X_1 + X_2) = E(X_1) + E(X_2)$ \\
$\text{Var}(X_1 + X_2) = \text{Var}(X_1) + \text{Var}(X_2) + 2\text{Cov}(X_1, X_2)$
%\sigma_1^2 + \sigma_2^2 + 2\rho\sigma_1\sigma_2
\\
Or, a normal distribution with mean $\mu_1 + \mu_2$ and variance $\text{Var}(X_1) + \text{Var}(X_2) + 2\text{Cov}(X_1, X_2)$.
%The sum of RVs making up the bivariate normal is a normal distribution itself, with parameters N(m1 + m2, Var(X1 + X2)). We have all the data form the mean vector mu, and covariance matrix sigma.

}

\end{document}